PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
Added chunks for ethnicity and started working on age.

# Demographics
## Ethnicity_collapsed
### Pie charts
**NEED TO CREATE ETHNICITY_collapsed variable**
```{r Ethnicity_collapsed prop per total summary}
Ethnicity_collapsed_prop_Covid <- dat.raw %>%
  count(Ethnicity_collapsed, covid_probable_case_incl_screening) %>%
  drop_na() %>%
  mutate(freq = round(n/sum(n), 2))

@@

```{r ethnicity pie chart biggest group label}
eth_pie_alllabel <- 
  Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")  +
    geom_text(aes(y = c(0.5),
                  label= c(paste0(round((freq[1]*100),0),"%"))), #Frequency of European only
             size=5,
             face="bold"
             )

eth_pie_alllabel
```

Pie chart - no labels

```{r ethnicity pie chart no label}
eth_pie_nolabel <- 
  Ethnicity_collapsed_prop_Sample %>%
   mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%

  ggplot(aes(x="", y=freq, fill=Ethnicity_collapsed)) +
  geom_bar(width = 1, stat = "identity") +
  scale_fill_manual(values =  COPINGpalette6) +
  scale_color_manual(values =  COPINGpalette6) +
  coord_polar("y",start=0) +
  theme_void() +
   labs(title = paste("RAMP/COPING sample self reported ethnicity",
                      sep=" "),
        subtitle = paste("n =", sum(Ethnicity_collapsed_prop_Sample$n),
                         sep = " "),
        fill = "Self reported ethnicity")

eth_pie_nolabel
```

>>>>

# Demographics

## Age
## Proportion tables
```{r age_category per Sample prop per total}
age_category_per_Covid_prop_total <- dat.raw %>%
  count(age_category, covid_probable_case_incl_screening) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(age_category_per_Covid_prop_total)
age_category_per_Covid_prop_total
```

```{r age_category per Sample prop per Sample}
age_category_per_Sample_prop_Sample <- dat %>%
  group_by(Sample) %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2))

kable(age_category_per_Sample_prop_Sample)
age_category_per_Sample_prop_Sample
```

## Cross tables
```{r age_category per Sample prop cross table}
age_category_per_Sample_prop_Sample_cross_table <- dat %>%
  group_by(Sample) %>%
  count(age_category, Sample) %>%
  mutate(Prop = round(n/sum(n), 2)) %>%
  pivot_wider(names_from = Sample, values_from = c(n, Prop))

kable(age_category_per_Sample_prop_Sample_cross_table)
age_category_per_Sample_prop_Sample_cross_table
```

## Sex

## Smoking

## BMI

## Key worker status

## Ethnicity_collapsed
### Pie charts
```{r Collapse Ethnicity}
dat.raw <- dat.raw %>%
  mutate(Ethnicity_collapsed_numeric =
           case_when(
             Ethnicity_numeric == 1 ~ 0, #European
             Ethnicity_numeric == 2 ~ 1, #Mixed or multiple ethnic origins 
             Ethnicity_numeric == 3 ~ 2, #Asian or Asian British
             Ethnicity_numeric == 4 ~ 3, #African or African British
             Ethnicity_numeric == 5 ~ 3, #Arab - combined with African/African British
             Ethnicity_numeric == 6 ~ 4  #Other ethnic group
           )
  )

dat.raw <- dat.raw %>%
  mutate(Ethnicity_collapsed =
           recode_factor(
             Ethnicity_collapsed_numeric,
             `0` = "European",
             `1` = "Mixed or multiple ethnic origins",
             `2` = "Asian or Asian British",
             `3` = "African or African British",
             `4` = "Other"
           )
  )

dat.raw %>%
  freq(Ethnicity_collapsed)
```

```{r Ethnicity_collapsed prop per total summary}
Ethnicity_collapsed_prop_Covid <- dat.raw %>%
  count(covid_probable_case_incl_screening, Ethnicity_collapsed) %>%
  drop_na() %>%
  mutate(freq = round(n/sum(n), 2))

@@

```{r ethnicity pie chart biggest group label}
Ethnicity_by_Covid_collapsed_count <- Ethnicity_collapsed_prop_Covid %>%
  mutate(Ethnicity_collapsed = fct_reorder(Ethnicity_collapsed,-n)) %>%
  group_by(covid_probable_case_incl_screening) %>% 
  ggplot(mapping = aes(
    x = Ethnicity_collapsed,
    y = n)
    ) +
  geom_bar(
    aes(fill = covid_probable_case_incl_screening),
    stat="identity",
    binwidth = 1,
    position = position_dodge2(preserve = "single")
  ) +
  labs(
    x = "Ethnicity",
    y = "Number of participants",
    fill = "Covid status") +
  theme_personal +
  scale_fill_manual(
    values = COPINGpalette4
    ) +
  coord_flip()

Ethnicity_by_Covid_collapsed_count
